---
title: "Amaizing  Baseline Survey_Final-rp_plot"
author: "Njambi"
format: html
editor: visual
---

## 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Clear the environment

```{r}

rm(list = ls())

```

## Loading necessary libraries

```{r, include=FALSE}

library(tidyverse) # includes the dplyr, ggplot2, tidyr, readr, stringr, forcats, tibble packages
library(readxl)
library(Hmisc)
library(labelled)
library(magrittr)
library(datawizard)
library(gtsummary)
library(gt)
library(kableExtra)
library(flextable)
library(splitstackshape)
library(lubridate)
library(foreign)
library(haven)


```

## Set the working directory

```{r}
# Set working directory

setwd("C:\\Users\\awanjau\\OneDrive - CGIAR\\Alliance\\Alliance_2024\\AMAZING\\AmazingBaselineDataCleaning\\Amaizing  Baseline Survey_Final-rp_plot")
      
```

## Loading data

```{r}
# Read a csv file

aMaizingBL_plot_path <- "C:\\Users\\awanjau\\OneDrive - CGIAR\\Alliance\\Alliance_2024\\AMAZING\\aMaizingBaseline_Files\\Amaizing  Baseline Survey_Final-rp_plot.csv"

aMaizingBL_plot <- read_csv(aMaizingBL_plot_path)

head(aMaizingBL_plot)
```

```{r}
# Check number of rows and columns in data

dim(aMaizingBL_plot)

# Print column names

names(aMaizingBL_plot)
```

```{r}
class(aMaizingBL_plot$calplotindex)

sort(unique(aMaizingBL_plot$calplotindex), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    calplotindex = as.integer(calplotindex)
  )

class(aMaizingBL_plot$calplotindex)
unique(aMaizingBL_plot$calplotindex)
```

```{r}
class(aMaizingBL_plot$e2)

#sort(unique(aMaizingBL_plot$e2), na.last = TRUE)
```

This is plot name; left as is.

```{r}
class(aMaizingBL_plot$plotid)

#sort(unique(aMaizingBL_plot$plotid), na.last = TRUE)
```

This column is the same as `e2`.\
Left as is.

```{r}
table(aMaizingBL_plot$plotid == aMaizingBL_plot$e2)
```

Since `aMaizingBL_plot$plotid == aMaizingBL_plot$e2`, drop `plotid` and remain with `e2`.

```{r}
class(aMaizingBL_plot$e3)

sort(unique(aMaizingBL_plot$e3), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$e4)

sort(unique(aMaizingBL_plot$e4), na.last = TRUE)
```

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e4 = factor(
      e4, 
      levels = c(1:3), 
      labels = c("Own",	"Rented in",	"Shared in")
    )
  
  ) 

class(aMaizingBL_plot$e4)
unique(aMaizingBL_plot$e4)
```

```{r}
class(aMaizingBL_plot$e51)

sort(unique(aMaizingBL_plot$e51), na.last = TRUE)
```

1 Male 2 Jointly 0 Female

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e51 = factor(
      e51, 
      levels = c(0:2), 
      labels = c("Female",	"Male",	"Jointly")
    )
  
  ) 

class(aMaizingBL_plot$e51)
unique(aMaizingBL_plot$e51)
```

```{r}
class(aMaizingBL_plot$e6)

sort(unique(aMaizingBL_plot$e6), na.last = TRUE)
```

1 Poor 2 Medium 3 Good

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e6 = factor(
      e6, 
      levels = c(1:3), 
      labels = c("Poor",	"Medium",	"Good"),
      ordered = TRUE
    )
  
  ) 

class(aMaizingBL_plot$e6)
unique(aMaizingBL_plot$e6)
```

```{r}
class(aMaizingBL_plot$e7)

sort(unique(aMaizingBL_plot$e7), na.last = TRUE)
```

1 Shallow 2 Medium 3 Deep

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e7 = factor(
      e7, 
      levels = c(1:3), 
      labels = c("Shallow",	"Medium",	"Deep"),
      ordered = TRUE
    )
  
  ) 

class(aMaizingBL_plot$e7)
unique(aMaizingBL_plot$e7)
```

```{r}
class(aMaizingBL_plot$e8)

sort(unique(aMaizingBL_plot$e8), na.last = TRUE)
```

1 Gently slope (flat) 2 Medium slope 3 Steep Slope

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e8 = factor(
      e8, 
      levels = c(1:3), 
      labels = c("Gently slope (flat)",	"Medium slope",	"Steep Slope"),
      ordered = TRUE
    )
  
  ) 

class(aMaizingBL_plot$e8)
unique(aMaizingBL_plot$e8)
```

```{r}
class(aMaizingBL_plot$e9)

sort(unique(aMaizingBL_plot$e9), na.last = TRUE)
```

***Confirm unit of measurement***

```{r}
class(aMaizingBL_plot$e10)

sort(unique(aMaizingBL_plot$e10), na.last = TRUE)
```

1 Yes 0 No -888 Don’t Know

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e10 = factor(
      e10, 
      levels = c(0:1), 
      labels = c("No", "Yes")
    )
  
  ) 

class(aMaizingBL_plot$e10)
unique(aMaizingBL_plot$e10)
```

```{r}
class(aMaizingBL_plot$e11)

sort(unique(aMaizingBL_plot$e11), na.last = TRUE)

# Text; multi-select column
```

```{r}
class(aMaizingBL_plot$e11_1)

sort(unique(aMaizingBL_plot$e11_1), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e11_1 = as.integer(e11_1)
  )

class(aMaizingBL_plot$e11_1)
unique(aMaizingBL_plot$e11_1)
```

```{r}
class(aMaizingBL_plot$e11_2)

sort(unique(aMaizingBL_plot$e11_2), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e11_2 = as.integer(e11_2)
  )

class(aMaizingBL_plot$e11_2)
unique(aMaizingBL_plot$e11_2)
```

```{r}
class(aMaizingBL_plot$e11_3)

sort(unique(aMaizingBL_plot$e11_3), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e11_3 = as.integer(e11_3)
  )

class(aMaizingBL_plot$e11_3)
unique(aMaizingBL_plot$e11_3)
```

```{r}
class(aMaizingBL_plot$e11_4)

sort(unique(aMaizingBL_plot$e11_4), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    e11_4 = as.integer(e11_4)
  )

class(aMaizingBL_plot$e11_4)
unique(aMaizingBL_plot$e11_4)
```

```{r}
class(aMaizingBL_plot$f7)

sort(unique(aMaizingBL_plot$f7), na.last = TRUE)

# Text; multi-select column
```

```{r}
class(aMaizingBL_plot$f7_1)

sort(unique(aMaizingBL_plot$f7_1), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_1 = as.integer(f7_1)
  )

class(aMaizingBL_plot$f7_1)
unique(aMaizingBL_plot$f7_1)
```

```{r}
class(aMaizingBL_plot$f7_2)

sort(unique(aMaizingBL_plot$f7_2), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_2 = as.integer(f7_2)
  )

class(aMaizingBL_plot$f7_2)
unique(aMaizingBL_plot$f7_2)
```

```{r}
class(aMaizingBL_plot$f7_3)

sort(unique(aMaizingBL_plot$f7_3), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_3 = as.integer(f7_3)
  )

class(aMaizingBL_plot$f7_3)
unique(aMaizingBL_plot$f7_3)
```

```{r}
class(aMaizingBL_plot$f7_4)

sort(unique(aMaizingBL_plot$f7_4), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_4 = as.integer(f7_4)
  )

class(aMaizingBL_plot$f7_4)
unique(aMaizingBL_plot$f7_4)
```

***Drop this column***

```{r}
class(aMaizingBL_plot$f7_5)

sort(unique(aMaizingBL_plot$f7_5), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_5 = as.integer(f7_5)
  )

class(aMaizingBL_plot$f7_5)
unique(aMaizingBL_plot$f7_5)
```

```{r}
class(aMaizingBL_plot$f7_6)

sort(unique(aMaizingBL_plot$f7_6), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_6 = as.integer(f7_6)
  )

class(aMaizingBL_plot$f7_6)
unique(aMaizingBL_plot$f7_6)
```

```{r}
class(aMaizingBL_plot$f7_7)

sort(unique(aMaizingBL_plot$f7_7), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_7 = as.integer(f7_7)
  )

class(aMaizingBL_plot$f7_7)
unique(aMaizingBL_plot$f7_7)
```

```{r}
class(aMaizingBL_plot$f7_8)

sort(unique(aMaizingBL_plot$f7_8), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_8 = as.integer(f7_8)
  )

class(aMaizingBL_plot$f7_8)
unique(aMaizingBL_plot$f7_8)
```

```{r}
class(aMaizingBL_plot$f7_9)

sort(unique(aMaizingBL_plot$f7_9), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_9 = as.integer(f7_9)
  )

class(aMaizingBL_plot$f7_9)
unique(aMaizingBL_plot$f7_9)
```

```{r}
class(aMaizingBL_plot$f7__666)

sort(unique(aMaizingBL_plot$f7__666), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7__666 = as.integer(f7__666)
  )

class(aMaizingBL_plot$f7__666)
unique(aMaizingBL_plot$f7__666)
```

```{r}
class(aMaizingBL_plot$f7__222)

sort(unique(aMaizingBL_plot$f7__222), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7__222 = as.integer(f7__222)
  )

class(aMaizingBL_plot$f7__222)
unique(aMaizingBL_plot$f7__222)
```

```{r}
class(aMaizingBL_plot$f7_sp)

sort(unique(aMaizingBL_plot$f7_sp), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f7_sp = case_when(
      f7_sp %in% c("Baraka", "Mavuno") ~ "Mavuno Baraka",
      TRUE ~ f7_sp
    ),
    
    f7_sp = factor(f7_sp)
  )

class(aMaizingBL_plot$f7_sp)
unique(aMaizingBL_plot$f7_sp)
```

```{r}
class(aMaizingBL_plot$fertilizer_count)

sort(unique(aMaizingBL_plot$fertilizer_count), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    fertilizer_count = as.integer(fertilizer_count)
  )

class(aMaizingBL_plot$fertilizer_count)
unique(aMaizingBL_plot$fertilizer_count)
```

```{r}
class(aMaizingBL_plot$`SET-OF-fertilizer`)

#sort(unique(aMaizingBL_plot$`SET-OF-fertilizer`), na.last = TRUE)

# ID column
```

```{r}
class(aMaizingBL_plot$f12)

sort(unique(aMaizingBL_plot$f12), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$f13)

sort(unique(aMaizingBL_plot$f13), na.last = TRUE)
```

1 liter 2 grams 3 Kilograms -222 Other, Specify

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f13 = factor(
      f13, 
      levels = c(1:3, -222), 
      labels = c("liter",	"grams",	"Kilograms", "Other, Specify")
    )
  
  ) 

class(aMaizingBL_plot$f13)
unique(aMaizingBL_plot$f13)
```

```{r}
class(aMaizingBL_plot$f13_sp)

sort(unique(aMaizingBL_plot$f13_sp), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f13_sp = case_when(
      f13_sp %in% c("Mililitre", "Millilitres" , "Ml") ~ "milliliter", 
      TRUE ~ f13_sp
    )
  )

class(aMaizingBL_plot$f13_sp)

sort(unique(aMaizingBL_plot$f13_sp), na.last = TRUE)
```

Drop f13_sp after replacing in f13.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(

    f13 = as.character(f13),
    f13 = str_replace_all(f13, "Other, Specify",
                                              replacement = f13_sp),
    f13 = factor(f13)
  )

class(aMaizingBL_plot$f13)
unique(aMaizingBL_plot$f13)

```

```{r}
class(aMaizingBL_plot$f14)
unique(aMaizingBL_plot$f14)
```

```{r}
class(aMaizingBL_plot$f15)
unique(aMaizingBL_plot$f15)
```

1 liter 2 grams 3 Kilograms -222 Other, Specify

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f15 = factor(
      f15, 
      levels = c(1:3, -222), 
      labels = c("liter",	"grams",	"Kilograms", "Other, Specify")
    )
  
  ) 

class(aMaizingBL_plot$f15)
unique(aMaizingBL_plot$f15)
```

```{r}
class(aMaizingBL_plot$f15_sp)
unique(aMaizingBL_plot$f15_sp)
```

```{r}
# Filter rows for which `f15_sp %in% c("50ml" , "40 millilitres")` and check corresponding entries for f14.

aMaizingBL_plot %>%
  filter(f15_sp %in% c("50ml" , "40 millilitres")) %>%
  select(PARENT_KEY, KEY, f14, f15, f15_sp)

# Mutate`f14` before replacing `f15_sp %in% c("50ml" , "40 millilitres")` with `milliliter`

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f14 = case_when(
      f15_sp %in% c("50ml" , "40 millilitres") ~ as.numeric(str_extract(f15_sp, "\\d+")) * f14, 
      
      TRUE ~ f14
    )
  )

# Filter again

aMaizingBL_plot %>%
  filter(f15_sp %in% c("50ml" , "40 millilitres")) %>%
  select(PARENT_KEY, KEY, f14, f15, f15_sp)


# Clean f15_sp

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f15_sp = case_when(
      f15_sp %in% c("Millitres", "Millilitres", "50ml", "Milliliters", "ML", "Ml", "Mills", "Mls", "40 millilitres") ~ "milliliter", 
      TRUE ~ f13_sp
    )
  )

class(aMaizingBL_plot$f15_sp)

sort(unique(aMaizingBL_plot$f15_sp), na.last = TRUE)
```

# Replace f15_sp in f15 and drop f15_sp

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(

    f15 = as.character(f15),
    f15 = str_replace_all(f15, "Other, Specify",
                                              replacement = f15_sp),
    f15 = factor(f15)
  )

class(aMaizingBL_plot$f15)
unique(aMaizingBL_plot$f15)

```

```{r}
class(aMaizingBL_plot$f14_fung)
unique(aMaizingBL_plot$f14_fung)
```

```{r}
class(aMaizingBL_plot$f15_fung)
unique(aMaizingBL_plot$f15_fung)
```

1 liter 2 grams 3 Kilograms -222 Other, Specify

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f15_fung = factor(
      f15_fung, 
      levels = c(1:3, -222), 
      labels = c("liter",	"grams",	"Kilograms", "Other, Specify")
    )
  
  ) 

class(aMaizingBL_plot$f15_fung)
unique(aMaizingBL_plot$f15_fung)
```

```{r}
class(aMaizingBL_plot$f15_fung_sp)
unique(aMaizingBL_plot$f15_fung_sp)
```

Drop `f15_fung_sp`; it is blank.

```{r}
class(aMaizingBL_plot$f20)
unique(aMaizingBL_plot$f20)
```

1 Yes 0 No

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f20 = factor(
      f20, 
      levels = c(0:1), 
      labels = c("No", "Yes")
    )
  
  ) 

class(aMaizingBL_plot$f20)
unique(aMaizingBL_plot$f20)
```

```{r}
class(aMaizingBL_plot$f20_1)
unique(aMaizingBL_plot$f20_1)
```

```{r}
aMaizingBL_plot %>%
  filter(f20_1 == 888.00)
```

```{r}
class(aMaizingBL_plot$f20_2)
sort(unique(aMaizingBL_plot$f20_2), na.last = TRUE)
```

unitmanu 1 Pickup unitmanu 2 Truck/Canter unitmanu 3 Wheelbarrow unitmanu 4 Tractor Carrier unitmanu 5 Gorogoro (2kgs) unitmanu 6 Debe (16Kgs) unitmanu 7 Bucket unitmanu 8 Kgs unitmanu -222 Other Specify

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f20_2 = factor(
      f20_2, 
      levels = c(1:8, -222), 
      labels = c("Pickup", "Truck/Canter", "Wheelbarrow", "Tractor Carrier", "Gorogoro (2kgs)", "Debe (16Kgs)", "Bucket", "Kgs", "Other Specify")
    )
  
  ) 

class(aMaizingBL_plot$f20_2)
unique(aMaizingBL_plot$f20_2)
```

```{r}
class(aMaizingBL_plot$f20_sp)
unique(aMaizingBL_plot$f20_sp)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    
    f20_sp = case_when(
      f20_sp %in% c("25kg bag", "25kg sacks") ~ "25Kg bag",
      f20_sp %in% c("90 kg bag","90 kgs bag", "90 kgs gunia", "90 kg bags", "90kgs bag", "90kg", "90 kg gunia", "90kg bags", "90 kgs bags", "90kg bag", "90 kg gunias", "90kg gunias") ~ "90Kg bag",
      f20_sp %in% c("50 kg gunias", "50kg sack", "50kgs bag", "50kg bag", "50kg bags", "50kg") ~ "50Kg bag",
      f20_sp == "100 Kg bag" ~ "100Kg bag",
      f20_sp %in% c("Cart", "Ox drawn cart", "Mkokoteni/cart", "Carts", "Animal drawn cart", "Animal drawn carts", "Donkey carts", "Mkokoteni", "Ox cart", "Ox carts") ~ "Animal-drawn cart",
      f20_sp %in% c("Uteo used to carry compost leaves from under trees in compound", "Basins", "Sacks") ~ NA_character_,
      
      TRUE ~ f20_sp
    )
  )


class(aMaizingBL_plot$f20_sp)
unique(aMaizingBL_plot$f20_sp)
```

Drop f20_sp after replacing in f20_2.

```{r}

aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(

    f20_2 = as.character(f20_2),
    f20_2 = str_replace_all(f20_2, "Other Specify",
                                              replacement = f20_sp),
    f20_2 = factor(f20_2)
  )

class(aMaizingBL_plot$f20_2)
unique(aMaizingBL_plot$f20_2)

```

```{r}

class(aMaizingBL_plot$preparation_mode)
unique(aMaizingBL_plot$preparation_mode)

# Multi-select
```

```{r}
class(aMaizingBL_plot$preparation_mode_1)
unique(aMaizingBL_plot$preparation_mode_1)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    preparation_mode_1 = as.integer(preparation_mode_1)
  )

class(aMaizingBL_plot$preparation_mode_1)
unique(aMaizingBL_plot$preparation_mode_1)
```

```{r}
class(aMaizingBL_plot$preparation_mode_2)
unique(aMaizingBL_plot$preparation_mode_2)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    preparation_mode_2 = as.integer(preparation_mode_2)
  )

class(aMaizingBL_plot$preparation_mode_2)
unique(aMaizingBL_plot$preparation_mode_2)
```

```{r}
class(aMaizingBL_plot$f17_preparation)
unique(aMaizingBL_plot$f17_preparation)
```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f17_preparation = as.integer(f17_preparation)
  )

class(aMaizingBL_plot$f17_preparation)
unique(aMaizingBL_plot$f17_preparation)
```

```{r}
class(aMaizingBL_plot$f16_preparation)
unique(aMaizingBL_plot$f16_preparation)
```

```{r}
class(aMaizingBL_plot$f18_preparation)
unique(aMaizingBL_plot$f18_preparation)
```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f18_preparation = as.integer(f18_preparation)
  )

class(aMaizingBL_plot$f18_preparation)
unique(aMaizingBL_plot$f18_preparation)
```

```{r}
class(aMaizingBL_plot$f19_preparation)
unique(aMaizingBL_plot$f19_preparation)
```

```{r}
class(aMaizingBL_plot$planting_mode)
unique(aMaizingBL_plot$planting_mode)

# Multi-select
```

```{r}
class(aMaizingBL_plot$planting_mode_1)
unique(aMaizingBL_plot$planting_mode_1)

```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    planting_mode_1 = as.integer(planting_mode_1)
  )

class(aMaizingBL_plot$planting_mode_1)
unique(aMaizingBL_plot$planting_mode_1)
```

```{r}
class(aMaizingBL_plot$planting_mode_2)
unique(aMaizingBL_plot$planting_mode_2)

```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    planting_mode_2 = as.integer(planting_mode_2)
  )

class(aMaizingBL_plot$planting_mode_2)
unique(aMaizingBL_plot$planting_mode_2)
```

```{r}
class(aMaizingBL_plot$f16_planting)
unique(aMaizingBL_plot$f16_planting)

```

```{r}
class(aMaizingBL_plot$f18_planting)
unique(aMaizingBL_plot$f18_planting)

```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f18_planting = as.integer(f18_planting)
  )

class(aMaizingBL_plot$f18_planting)
unique(aMaizingBL_plot$f18_planting)
```

```{r}
class(aMaizingBL_plot$f19_planting)
unique(aMaizingBL_plot$f19_planting)
```

```{r}
class(aMaizingBL_plot$weeding_mode)
unique(aMaizingBL_plot$weeding_mode)

# Multi-select
```

```{r}
class(aMaizingBL_plot$weeding_mode_1)
unique(aMaizingBL_plot$weeding_mode_1)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    weeding_mode_1 = as.integer(weeding_mode_1)
  )

class(aMaizingBL_plot$weeding_mode_1)
unique(aMaizingBL_plot$weeding_mode_1)
```

```{r}
class(aMaizingBL_plot$weeding_mode_2)
unique(aMaizingBL_plot$weeding_mode_2)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    weeding_mode_2 = as.integer(weeding_mode_2)
  )

class(aMaizingBL_plot$weeding_mode_2)
unique(aMaizingBL_plot$weeding_mode_2)
```

```{r}
class(aMaizingBL_plot$f17_weeding)
unique(aMaizingBL_plot$f17_weeding)
```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f17_weeding = as.integer(f17_weeding)
  )

class(aMaizingBL_plot$f17_weeding)
unique(aMaizingBL_plot$f17_weeding)
```

```{r}
class(aMaizingBL_plot$f16_weeding)
unique(aMaizingBL_plot$f16_weeding)
```

```{r}
class(aMaizingBL_plot$f18_weeding)
unique(aMaizingBL_plot$f18_weeding)
```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f18_weeding = as.integer(f18_weeding)
  )

class(aMaizingBL_plot$f18_weeding)
unique(aMaizingBL_plot$f18_weeding)
```

```{r}
class(aMaizingBL_plot$f19_weeding)
unique(aMaizingBL_plot$f19_weeding)
```

```{r}
class(aMaizingBL_plot$harvest_mode)
unique(aMaizingBL_plot$harvest_mode)

# Multi-select
```

```{r}
class(aMaizingBL_plot$harvest_mode_1)
unique(aMaizingBL_plot$harvest_mode_1)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    harvest_mode_1 = as.integer(harvest_mode_1)
  )

class(aMaizingBL_plot$harvest_mode_1)
unique(aMaizingBL_plot$harvest_mode_1)
```

```{r}
class(aMaizingBL_plot$harvest_mode_2)
unique(aMaizingBL_plot$harvest_mode_2)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    harvest_mode_2 = as.integer(harvest_mode_2)
  )

class(aMaizingBL_plot$harvest_mode_2)
unique(aMaizingBL_plot$harvest_mode_2)
```

```{r}
class(aMaizingBL_plot$f16_harvesting)
unique(aMaizingBL_plot$f16_harvesting)
```

```{r}
class(aMaizingBL_plot$f18_harvesting)
sort(unique(aMaizingBL_plot$f18_harvesting), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f18_harvesting = as.integer(f18_harvesting)
  )

class(aMaizingBL_plot$f18_harvesting)
sort(unique(aMaizingBL_plot$f18_harvesting), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$f19_harvesting)
sort(unique(aMaizingBL_plot$f19_harvesting), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$threshing_mode)
sort(unique(aMaizingBL_plot$threshing_mode), na.last = TRUE)

# Multi-select
```

```{r}
class(aMaizingBL_plot$threshing_mode_1)
sort(unique(aMaizingBL_plot$threshing_mode_1), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    threshing_mode_1 = as.integer(threshing_mode_1)
  )

class(aMaizingBL_plot$threshing_mode_1)
sort(unique(aMaizingBL_plot$threshing_mode_1), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$threshing_mode_2)
sort(unique(aMaizingBL_plot$threshing_mode_2), na.last = TRUE)
```

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    threshing_mode_2 = as.integer(threshing_mode_2)
  )

class(aMaizingBL_plot$threshing_mode_2)
sort(unique(aMaizingBL_plot$threshing_mode_2), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$f16_threshing)
sort(unique(aMaizingBL_plot$f16_threshing), na.last = TRUE)
```

```{r}
class(aMaizingBL_plot$f18_threshing)
sort(unique(aMaizingBL_plot$f18_threshing), na.last = TRUE)
```

Questionnaire defines it as numeric, but converted to integer during cleaning.

```{r}
aMaizingBL_plot <- aMaizingBL_plot %>%
  mutate(
    f18_threshing = as.integer(f18_threshing)
  )

class(aMaizingBL_plot$f18_threshing)
unique(aMaizingBL_plot$f18_threshing)
```

```{r}
class(aMaizingBL_plot$f19_threshing)
sort(unique(aMaizingBL_plot$f19_threshing), na.last = TRUE)
```

```{r}

column_labels <- c(
  
  calplotindex = "Plot index",
  e2 = "Plot name",
  # plotid = "Plot name",
  e3 = "What is the size of plotid",
  e4 = "Ownership of plotid",
  e51 = "Who manages plotid",
  e6 = "Soil fertility of plotid",
  e7 = "Soil depth of plotid",
  e8 = "Land slope of plotid",
  e9  = "Whats the walking distance from plotid to residence",
  e10 = "Do you practice irrigation on plotid",
  e11 = "Who worked on your land",
  e11_1 = "Female household member",
  e11_2 = "Male household member",
  e11_3 = "Hired Labour",
  e11_4 = "Community (Shared) Labour",
  f7 = "Which type of fertilizer did you use in plotid?",
  f7_1 = "CAN",
  f7_2 = "DAP",
  f7_3 = "NPK",
  #f7_4 = "TSP",
  f7_5 = "Rock Phosphate",
  f7_6 = "Urea",
  f7_7 = "Branded fertilizer blends (Yara)",
  f7_8 = "Lime",
  f7_9 = "Foliar Fertilizer",
  f7__666 = "None of the above",
  f7__222 = "Other Specify",
  f7_sp = "Please Specify",
  fertilizer_count = "Count of type of fertilizer did you use in plotid",
  `SET-OF-fertilizer` = "Fertilizer repeat group ID",
  f12 = "Quantity of Herbicide used  in plotid",
  f13 = "Unit of Herbicides used  in plotid",
  #f13_sp = "Please Specify",
  f14 = "Quantity of Pesticide used in plotid",
  f15 = "Unit of Pesticide used in plotid",
  #f15_sp = "Please Specify",
  f14_fung = "Quantity of Fungicide used in plotid",
  f15_fung = "Unit of Fungicide used in plotid",
  #f15_fung_sp = "Please Specify",
  f20 = "Did you use organic manure  in plotid",
  f20_1 = "Quantity of manure utilized in plotid",
  f20_2 = "Unit of Manure used  in plotid",
  #f20_sp = "Please specify the Unit",
  preparation_mode = "Mode of land preparation?",
  preparation_mode_1 = "Manual Land Preparation",
  preparation_mode_2 = "Tractor or Animal drawn",
  f17_preparation = "How many times did you carry out  Land Preparation in plotid",
  f16_preparation = "How many days did you spend on  Land Preparation  in plotid",
  f18_preparation = "How many were you while  Land Preparation  in plotid",
  f19_preparation = "On average, How many hours per day did you spend on  Land Preparation  in plotid",
  planting_mode = "Mode of Land Planting",
  planting_mode_1 = "Manual",
  planting_mode_2 = "Mechanized",
  f16_planting = "How many days did you spend on  Planting  in plotid",
  f18_planting = "How many were you while  Planting  in plotid",
  f19_planting = "On average, How many hours per day did you spend on  Planting  in plotid",
  weeding_mode = "Mode of Weeding",
  weeding_mode_1 = "Manual",
  weeding_mode_2 = "Mechanized",
  f17_weeding = "How many times did you carry out  Weeding in plotid",
  f16_weeding = "How many days did you spend on  Weeding  in plotid",
  f18_weeding = "How many were you while  Weeding  in plotid",
  f19_weeding = "On average, How many hours per day did you spend on  Weeding  in plotid",
  harvest_mode = "Mode of Harvesting",
  harvest_mode_1 = "Manual",
  harvest_mode_2 = "Mechanized",
  f16_harvesting = "How many days did you spend on  Harvesting  in plotid",
  f18_harvesting = "How many were you while  Harvesting  in plotid",
  f19_harvesting = "On average, How many hours per day did you spend on  Harvesting  in plotid",
  threshing_mode = "Mode of Threshing?",
  threshing_mode_1 = "Manual threshing",
  threshing_mode_2 = "Mechanised Threshing",
  f16_threshing = "How many days did you spend on  Threshing  in plotid",
  f18_threshing = "How many were you while  Threshing  in plotid",
  f19_threshing = "On average, How many hours per day did you spend on  Threshing  in plotid",
  PARENT_KEY = "Parent key",
  KEY = "Key",
  `SET-OF-rp_plot` = "Plot repeat group ID"

)

```

```{r}

# Rename columns with characters not supported by stata

aMaizingBL_plot <- aMaizingBL_plot %>%
  
  rename(
    SET_OF_fertilizer = `SET-OF-fertilizer`,
    SET_OF_rp_plot = `SET-OF-rp_plot`
    
         )

```

```{r}
#names(aMaizingBL_plot)

aMaizingBL_plot <- aMaizingBL_plot %>%
  select(-c(3, 21, 34, 37, 40, 44)) %>%
  set_variable_labels(.labels = column_labels)

#names(aMaizingBL_plot)
```

Using the function View() to open the new data in a spreadsheet reveals the column names and labels.

```{r}

#View(aMaizingBL_plot)

```

## Generate a data dictionary

```{r}
# Data dictionary

aMaizingBL_plot_dict <- look_for(aMaizingBL_plot, labels = TRUE, values = TRUE) %>%
  dplyr::select(-c(missing, value_labels))

  gt(aMaizingBL_plot_dict)

```

## Export data dictionary to CSV

```{r}

readr::write_csv(aMaizingBL_plot_dict, "aMaizingBL_plot_dict.csv")

```

## Export data to CSV

```{r}

readr::write_csv(aMaizingBL_plot, "aMaizingBL_plot.csv")

```

## Save as R data

```{r}

save(aMaizingBL_plot, file = "aMaizingBL_plot.RData")
```

## Export data to SPSS

```{r}

write.foreign(aMaizingBL_plot, "aMaizingBL_plot.sav", "aMaizingBL_plot", package = "SPSS")

```

## Export data to STATA

```{r}

write_dta(aMaizingBL_plot, "aMaizingBL_plot.dta")

```
